Multispecies survey specifications

### 2020-10-29 msSurveysTest.Rmd
add new survey specifications, not run yet

>>>>

## Specifying a more realistic survey.

### New survey and fishery config files

`mssurvey_spring_01.R` and `mssurvey_fall_01.R` configure the fishery independent surveys. We keep spring and fall survey timing, but now we have efficiency defined for each species and a selectivity function for each species. Our surveys exclude offshore areas. These specifications are invented for demonstration purposes, not intended to realistically mimic a particular survey:

```{r, code = readLines("./config/mssurvey_spring_01.R"), eval=F}
```

```{r, code = readLines("./config/mssurvey_fall_01.R"), eval=F}
```

`msfishery_01.R` configures the fishery dependent data:

```{r, code = readLines("./config/msfishery_01.R"), eval=F}
```

Model boxes show where our survey works now. We are including boxes x...x in these surveys:
```{r NOBAmap}
knitr::include_graphics("images/NOBAboxes.png")
```

The way sampling is set up, effective N for each survey is the number of fish measured for length, age, and average weight at age. We could introduce further realism by using the `sample_ages()` function to take a subsample for age composition and optionally apply an ageing error matrix. This would require changing the `om_comps()` wrapper: see [atlantisom issue](https://github.com/r4atlantis/atlantisom/issues/42).

### New survey and fishery outputs

```{r full-test, message=FALSE, warning=FALSE, eval=FALSE}

#NOBAom <- om_init(here("config/NOBA2config.R"))

#NOBAom_ms <- om_species(sppsubset$Name, NOBAom)

NOBAom_ms <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))

# new wrapper for multiple surveys saves survey output separately
# but returns a list with all surveys, not ideal; make consistent

NOBAom_ms_ind <- om_index(usersurvey = c(here("config/mssurvey_spring_01.R"), 
                                         here("config/mssurvey_fall_01.R")), 
                           userfishery = here("config/msfishery_01.R"),
                           omlist_ss = NOBAom_ms, 
                           n_reps = 1, 
                           save = TRUE)

NOBAom_ms_comp <- om_comps(usersurvey = c(here("config/mssurvey_spring_01.R"), 
                                         here("config/mssurvey_fall_01.R")), 
                           userfishery = here("config/msfishery_01.R"),
                           omlist_ss = NOBAom_ms, 
                           n_reps = 1, 
                           save = TRUE)
